

\begin{thebibliography}{9}

%\bibitem{Agr}  I.~Agricola, {\em Old and New on the Exceptional Group},  Notices Amer. Math. Soc.
%{\bf 55}  (2008), no. 8, 922-929

\bibitem{Agr} A.A.~Agrachev, {\em  Rolling balls and octonions,} Proc. Steklov Inst.  Math. {\bf 258} 1 (2007): 13-22.



\bibitem{A}  D.~Alekseevsky, C.~Medori,  A.~Tomassini, 
{\em Homogeneous para-K\"ahler Einstein manifolds},
Russ. Math. Surv. {\bf 64 } (1) (2009) 3-50

%\bibitem{AG}  M.A. Akivis, V.V. Goldberg, 
%{\em Conformal differential geometry and Its generalizations}, Wiley-Interscience Publication, New York (1996)

\bibitem{AN} D.~An, P.~Nurowski,
{\em Twistor space for rolling bodies}, Comm. Math. Phys. {\bf 326.2} (2014), 393-414

%\bibitem{Bat}C.~Batista,  {\em  Weyl tensor classification in four-dimensional manifolds of all signatures}, General Relativity and Gravitation, 45(4) (2013), 785-798

\bibitem{BM}  G.~Bor, R.~Montomery, 
{\em $G_2$ and the ``rolling distribution"},   L'Ens. Math. {\bf 55} (2009), 157-196

\bibitem{BrHs} R.~Bryant, L.~Hsu,
{\em Rigidity of integral curves of rank 2 distributions}, Invent. Math. {\bf 114.1} (1993), 435-461

%\bibitem{BaHu} J.~Baez, J.~Huerta,
%{\em $G_2$ and rolling balls},  Trans.  AMS {\bf 366.10} (2014),  5257-5293

%\let\c\undefined

\bibitem{Cbook}  \'E.~Cartan, 
{\em Le\c{c}ons sur la th\'eorie des espaces \`a connexion projective}, Paris, Gauthier-Villars, 1937
	


\bibitem{C_thesis} \'E.~Cartan, 
{\em Sur la structure des groupes de transformations finis et continus}, Th\`ese, Paris, Nony 1894; 2e \'edition, Vuibert, 1933. (Reprinted also in \OE uvres Compl\`etes, Partie I, Volume 1, 137-288)


\bibitem{C_5var}  \'E.~Cartan,
{\em Les syst\`emes de Pfaff \`a cinq variables et les \'equations aux d\'eriv\'ees partielles du second ordre}, Ann. \'Ec. Norm. {\bf 27} (1910), 109-192

\bibitem{C1}  \'E.~Cartan,
{\em Sur la structure des groupes finis et continus},
 C.R. Acad. Sci. Paris {\bf 116}  (1893), 784-786


\bibitem{Ca3}  \'E.~Cartan, 
{\em Nombres complexes}, Encyclop. Sc. Math. (\'edition francaise) I 5, d'apr\'es l'article allemand de E. Study, 1908

\bibitem{CFG} V.~Cruceanu, P.~Fortuny, P.M.~ Gadea,
{\em A Survey on paracomplex geometry},
  Rocky Mountain J. Math. {\bf 26} (1996), no. 1, 83-115





\bibitem{DZ}B.~Doubrov, I.~Zelenko,
{\em Geometry of curves in parabolic homogeneous spaces},  arXiv preprint arXiv:1110.0226 (2011)

\bibitem{Eng} F.~Engel, 
{\em Sur un groupe simple \`a quatorze param\`etres},
 C.R. Acad. Sci. Paris  {\bf 116} (1893), 786-788



\bibitem{GTT} E.~Ghys,   S.~Tabachnikov,  V.~Timorin,
{\em Osculating curves: around the Tait-Kneser Theorem},  Math. Intelligencer {\bf 35}, No 1 (2013), 61-66

\bibitem{GHN}R.~Gover, D.~Hill, P.~Nurowski, {\em Sharp version of the Goldberg-Sachs theorem},
Annali di Matematica {\bf  190} (2011), 295-340

\bibitem{K}, I.~Kaplansky, {\em Linear algebra and geometry: a second course},  Courier Corporation, 1974.

\bibitem{KN} A.~Knapp, 
{\em Lie groups beyond an introduction}, Vol. 140. Springer Science \& Business Media, 2013.


\bibitem{KL} N. G.~Konovenko, V. V.~Lychagin,
{\em On projective classification of plane curves}, Global and Stochastic Anal. {\bf 1.2} (2011), 241-264


\bibitem{KLie} F.~Klein, S.~Lie,
{\em Ueber diejenigen ebenen Curven, welche durch ein geschlossenes System von einfach unendlich vielen vertauschbaren linearen Transformationen in sich \"ubergehen},  Math. Ann. {\bf 4.1} (1871), 50-84

\bibitem{N} P.~Nurowski, {\em Differential equations and conformal structures}, Journ. Geom. Phys. {\bf 55} 1 (2005), 19-49 


\bibitem{O}P.~Olver, {\em  Moving frames and differential invariants in centro-affine geometry}, Lobachevskii Journal of Mathematics {\bf 31.2}  (2010), 77-89.


\bibitem{OT} V.~Ovsienko, S.~Tabachnikov,
{\em Projective Differential Geometry Old and New: From the Schwarzian Derivative to the Cohomology of Diffeomorphism Groups}, Cambridge University Press, Cambridge Tracts in Mathematics, 165, 2005. (Available also online on the web page of the first author)

\bibitem{Pen}R.~Penrose, {\em Nonlinear Gravitons and Curved Twistor Theory},  General Relativity and Gravitation 7.1 (1976), 31Ð52.



\bibitem{Katja}K.~Sagerschnig, {\em Split octonions and generic rank two distributions in dimension five},  Arch. Math.(Brno) {\bf 42} suppl. (2006), 329-339.


\bibitem{ST}I.M.~Singer, Isadore, J.A.~Thorpe. {\em The curvature of 4-dimensional Einstein spaces}, Global Analysis (Papers in Honor of K. Kodaira), 1969, 355-365.



\bibitem{W} E.J.~Wilczynski, 
{\em Projective Differential Geometry of Curves and Ruled Surfaces},  Vol. 18. BG Teubner, 1906


\bibitem{Zel} I.~Zelenko, 
{\em On variational approach to differential invariants of rank two distributions},  Differential Geom. Appl. {\bf 24} (2006), no. 3, 235-259

\bibitem{Z} M.~Zorn,
{\em Theorie der alternativen Ringe},
{\bf 8} (1931), Abh. Math. Sem. Univ. Hamburg, 123-147



\end{thebibliography}









